Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2018-12-20 ms5n17-tlp-mn-180216-001.tex
Need help for results

The probe circuit was compiled in KiCAD to design the PCB layout. The PCB layout was provided to beta-layout (Aarbergen Germany) and P.W. Circuits LTD (Wigston , UK) to manufacture the PCBs. Easily and inexpensively available FR4 was used for PCB manufacturing for (figure~\ref{fig:ProbePhoto} A). Rogers RO35 from rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par

@@

Although FR4 is a cheap and quickly available material, inhomogeneities were observed in B$_0$ field images made from this PCBs. Better resolution can be achieved using Rogers RO35 from rogers corporation.

>>>>

The probe circuit was compiled in KiCAD to design the PCB layout. The PCB layout was provided to beta-layout (Aarbergen Germany) and P.W. Circuits LTD (Wigston , UK) to manufacture the PCBs. Easily and inexpensively available FR4 was used for PCB manufacturing for (figure~\ref{fig:ProbePhoto} A). Rogers RO3035 from rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par

@@

Initially FR4 PCB material was used to make detector assembly because of its low cost and easy availability. B$_0$ field maps of the sample chamber generated from gradient echo images using these detectors showed inhomogeneities in the B$_0$ field. To avoid inhomogeneities and therefore to achieve better resolution, detectors were made from RO3035 material from Rogers corporation. Though RO3035 provides better resolution it is more expensive and takes longer to obtain compared to FR4. A new detector design can first be tested using FR4 material and the optimised design can be made from RO3035.
